In this section, we will first define procedures and protocols to construct Mimblewimble transactions and prove their security.
The formalizations will be similar to those found by Fuchsbauer et al. in their cryptographic investigation of the mimblewimble \todo{Be consistent, always in capitals or always in lower letters} protocol~\cite{fuchsbauer2019aggregate}.
In particular the final transaction output by one of our protocols should be a valid transaction as by the definitions of Fuchsbauer et al.
As we will only focus on the transaction protocol (transferring value from one or many parties to one or many parties), the notions of transaction aggregation, coin minting and adding transactions to the main ledger discussed in~\cite{fuchsbauer2019aggregate} will not be topic of this formalization.

\todo[inline]{Check that all these concepts such as transaction aggregation, coin minting, etc... have been defined before (and probably add a reference to that section here). Otherwise, the reader gets lost here.}

As an extension to the regular transaction protocol transferring value from one sender to a receiver we will define two further schemes.
The first of them titled \emph{Extended Mimblewimble Transaction Scheme} will provide additional functions to create and spend coins owned by two parties instead of just one, thereby enabling coins owned by mutliple parties at once, which is similar to a mutlisig address in Bitcoin~\cite{antonopoulos2014mastering}.
The second extended definition is called \emph{Contract Mimblewimble Transaction Scheme} and will allow the receiver
of a coin to hide a secret witness value $\varWit$ in his part \todo{his part of what? what is a part here} of the transaction, in a way that the sender (or the senders) can redeem this secret after the protocol has completed and the final transaction is available.

We will proceed by providing an instantiation of the three \todo{three? in previous paragraph you only mentioned two} transactions schemes in section~\ref{sec:atom:inst} which can be implemented and deployed on a Mimblewimble based Cryptocurrency such as Beam or Grin.
In section~\ref{sec:atom:protocols} we define two-party protocols from the outlined schemes to construct mimbewimble transactions.
Section~\ref{sec:atom:security} shows the proofs that the schemes are correct and the protocols secure in the malicious setting as defined in definition~\ref{subsec:pre:security}.
Finally, in~\ref{sec:atom:atomic-swap}, we define a Atomic Swap protocol from these building blocks, allowing two parties to securely and trustlessly swap funds from a mimblewimble based blockchain with those on another blockchain, such as Bitcoin.

\section{Definitions}\label{sec:atom:definitions}
\input{chapters/adaptor_signature_based_atomic_swaps_between_bitcoin_and_mimblewimble/definitions}

\section{Instantiation}\label{sec:atom:inst}
\input{chapters/adaptor_signature_based_atomic_swaps_between_bitcoin_and_mimblewimble/instantiation}

\section{Protocols}\label{sec:atom:protocols}
\input{chapters/adaptor_signature_based_atomic_swaps_between_bitcoin_and_mimblewimble/protocols}

\section{Security \& Correctness} \label{sec:atom:security}
\input{chapters/adaptor_signature_based_atomic_swaps_between_bitcoin_and_mimblewimble/security-correctness}

\section{Atomic Swap protocol}\label{sec:atom:atomic-swap}
\input{chapters/adaptor_signature_based_atomic_swaps_between_bitcoin_and_mimblewimble/atomic-swap-protocol}